\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
Tried to add a summary for DMN.

It has been hypothesized that the adaptive role of memory retrieval is to facilitate 
construction of episodes to prepare for immediate and distant future scenarios.
So the DMN is involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

>>>>

It has been hypothesized that the adaptive role of memory retrieval is to facilitate 
construction of episodes to prepare for immediate and distant future scenarios. \cite{defaultnetworkadaptive}
The DMN is therefore involved in remembering the past, imagining the future, and story
comprehension. \cite{defaultnetworkadaptive}

Now, that we know a little bit about this default mode network, how does it pertain
to meditative practices. 
The DMN is the network that lends itself to excessive rumination. 
So when I sit down to meditate and my thoughts wander away (and how they wander!),
it is the DMN that is being activated.
